### 2022-06-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@6e83254033e0832aa8e4a280510cbc570cdcdc62 🚀

Under this framework, other regions where high viral sharing dominates
coevolutionary dynamics---such as Latin America, or Eurasia above a
northing of 30---would pose less of a risk of zoonotic emergence.
Nevertheless, areas of high host uniqueness coupled with high viral
sharing (red-to-pink in fig.~\ref{fig:trivariate}) could create hotspots
facilitated by viral codivergence. Our framework identifies Madagascar,
where most bat species are endemic following evolutionary divergence
from sister species in both African and Asian
continents,\textsuperscript{24} as one such hotspot; interestingly, a
recent study\textsuperscript{25} reported a novel and highly divergent
lineage of nobecoviruses from Madagascar-endemic pteropid bat species
(\emph{Pteropus rufus} and \emph{Rousettus madagascariensis}), again
supporting the predictive power of the coevolutionary framework.

>>>>

Compared to approaches that map emergence risk based only on the number
of known bat hosts of betacoronaviruses, our framework suggests regions
where high viral sharing dominates coevolutionary dynamics---such as
Latin America, or Eurasia above a northing of 30---would pose less of a
relative risk of zoonotic emergence. Nevertheless, areas of high host
uniqueness coupled with high viral sharing (red-to-pink in
fig.~\ref{fig:trivariate}) could create hotspots facilitated by viral
codivergence. Our framework identifies Madagascar, where most bat
species are endemic following evolutionary divergence from sister
species in both African and Asian continents,\textsuperscript{24} as one
such hotspot; interestingly, a recent study\textsuperscript{25} reported
a novel and highly divergent lineage of nobecoviruses from
Madagascar-endemic pteropid bat species (\emph{Pteropus rufus} and
\emph{Rousettus madagascariensis}), again supporting the predictive
power of the coevolutionary framework.
